Transparency in Science

### 2023-05-15 presentation.Rmd
start with a high level summary

---
class: inverse, center, middle

@@

---
background-image: url("images/contribution.svg")
background-position: center
background-size: contain
---

>>>>

---
background-image: url("images/contribution.svg")
background-position: center
background-size: contain

---
class: center, middle, inverse

.large.red[Human]   .Huge.yellow[Bias]   .large.red[Machine]

.large.red[Preregistration]   .Huge.yellow[Induction]   .large.red[Reproducibility]

@@

---
background-image: url("images/contribution.svg")
background-position: center
background-size: contain
